\documentclass[11pt,a4paper]{article}

\usepackage[margin=2.2cm]{geometry}
\usepackage{array}
\usepackage{longtable}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}

\definecolor{pmoteal}{HTML}{2F6F73}
\definecolor{pmoamber}{HTML}{D99A2B}
\definecolor{pmogray}{HTML}{405059}

\hypersetup{
  colorlinks=true,
  linkcolor=pmoteal,
  urlcolor=pmoteal
}

\setlist[itemize]{leftmargin=1.4em}
\setlist[enumerate]{leftmargin=1.6em}
\renewcommand{\arraystretch}{1.25}

\title{\textbf{Lecture Syllabus}\\From Plan to Control: Managing a Project Like a Real PMO}
\author{AI-Assisted Gamified Project Management Module}
\date{}

\begin{document}
\maketitle

\section*{Lecture Information}

\begin{tabular}{>{\bfseries}p{4cm}p{10.5cm}}
Module type & Gamified AI-assisted university lecture \\
Target audience & Licence/Master students in engineering, computer science, business, or management \\
Duration & One 3-hour session, or two 90-minute sessions \\
Main case & Smart Campus Mobile App project \\
License & CC-BY-NC recommended \\
\end{tabular}

\section*{Lecture Description}

In this lecture, students act as a project management office team responsible for delivering a Smart Campus Mobile App in 12 weeks. Students define project scope, identify stakeholders, build a Work Breakdown Structure, prepare a schedule, analyze dashboard indicators, face a project crisis, and present a corrective action plan.

\section*{Learning Objectives}

\begin{enumerate}
  \item Explain the project management cycle: initiation, planning, execution, monitoring, control, and closing.
  \item Build a deliverable-oriented Work Breakdown Structure for a realistic project.
  \item Convert a WBS into tasks, dependencies, milestones, and deliverables.
  \item Estimate duration, cost, resources, and risks.
  \item Optimize project execution by adjusting resources, sequencing, and priorities.
  \item Track progress using planned value, earned value, actual cost, SV, CV, SPI, and CPI.
  \item Diagnose project problems from dashboard data.
  \item Propose corrective actions when a project is late, over budget, or technically unstable.
  \item Communicate project status in a professional PMO-style briefing.
\end{enumerate}

\section*{Case Scenario}

The university wants to build a Smart Campus Mobile App in 12 weeks. The app includes student login, course schedule, exam calendar, notifications, room reservation, complaint/request system, admin dashboard, and pilot deployment.

\section*{Project Constraints}

\begin{tabular}{>{\bfseries}p{4cm}p{10.5cm}}
Budget & 40,000 USD \\
Duration & 12 weeks \\
Team & 1 project manager, 2 backend developers, 2 mobile developers, 1 UI/UX designer, 1 QA tester \\
Main risk & Integration delay with the university database \\
Sponsor pressure & First demo required by week 6 \\
\end{tabular}

\section*{Gamified Progression}

\begin{longtable}{>{\bfseries}p{1.6cm}p{3.2cm}p{5.2cm}p{3.4cm}}
\textbf{Level} & \textbf{Name} & \textbf{Mission} & \textbf{Badge} \\
\hline
1 & Project Launch & Define scope, stakeholders, constraints, and success criteria & Scope Master \\
2 & WBS Builder & Build a deliverable-oriented WBS & WBS Architect \\
3 & Schedule Rescue & Compress a 15-week plan into a realistic 12-week schedule & Schedule Optimizer \\
4 & Dashboard Detective & Analyze week 6 dashboard data and diagnose project health & Dashboard Detective \\
5 & Crisis Controller & Respond to the week 8 crisis and present a recovery briefing & Risk Analyst / Crisis Controller \\
\end{longtable}

\section*{Lecture Schedule}

\begin{longtable}{>{\bfseries}p{2.5cm}p{5.1cm}p{4cm}p{3cm}}
\textbf{Time} & \textbf{Activity} & \textbf{Learning Type} & \textbf{Tools} \\
\hline
0--15 min & Opening scenario and decision poll & Acquisition + discussion & Genially, Mentimeter/Wooclap \\
15--45 min & Planning concepts and project charter & Acquisition + inquiry & Slides, NotebookLM \\
45--80 min & WBS workshop & Production + collaboration & Worksheet, Canva, Mermaid/draw.io \\
80--90 min & Break & Pause & -- \\
90--120 min & Schedule optimization challenge & Practice + collaboration & Google Sheets/Excel \\
120--155 min & Dashboard and KPI analysis & Practice + inquiry & Google Sheets, Quizizz \\
155--175 min & Week 8 crisis simulation & Discussion + production & Genially, group briefing \\
175--180 min & Exit ticket & Reflection & Google Forms or paper \\
\end{longtable}

\section*{Assessment}

\begin{longtable}{>{\bfseries}p{6cm}p{3cm}p{5.3cm}}
\textbf{Criterion} & \textbf{Weight} & \textbf{Focus} \\
\hline
Scope clarity & 15\% & Stakeholders, constraints, and measurable success criteria \\
WBS quality & 20\% & Deliverable orientation, completeness, and logical decomposition \\
Schedule and dependencies & 20\% & Realistic sequencing, dependencies, and optimization \\
Risk analysis & 15\% & Identification of risks and relevant mitigation actions \\
Tracking and control logic & 20\% & Correct dashboard interpretation and corrective action reasoning \\
Professional presentation & 10\% & Clear, concise, and convincing PMO briefing \\
\end{longtable}

\end{document}
