\documentclass[11pt,a4paper]{article}
\usepackage{pmo_activity_handout}

\hypersetup{colorlinks=true,urlcolor=pmoTeal,pdftitle={PMO Recovery Briefing Production Studio},pdfauthor={Mohamad Aoude}}
\rhead{Production Exercise}

\begin{document}

\activitytitle{PRODUCTION ACTIVITY}{PMO Recovery Briefing Studio}{Create a Sponsor-Ready Project Artifact}{Duration: 30 minutes \quad | \quad Work: PMO team of 4--5 \quad | \quad Output: written and oral recovery briefing}

\begin{activitybox}
\textbf{Production mission.} Transform your charter, WBS, schedule, dashboard diagnosis, and crisis decision into one professional recovery briefing. The final product must enable the sponsor to understand the issue and make a specific decision.
\end{activitybox}

\section{1. Required Product}

Produce a one-page written briefing and a maximum three-minute oral presentation containing:

\begin{enumerate}
  \item executive status and evidence;
  \item root cause or clearly labeled uncertainty;
  \item impact on scope, schedule, cost, quality, risk, and stakeholders;
  \item recommended corrective actions;
  \item revised pilot scope and milestone plan;
  \item monitoring indicators and escalation thresholds; and
  \item one explicit sponsor decision request.
\end{enumerate}

\section{2. Product Standards}

The artifact must be concise, evidence-based, feasible, transparent about uncertainty, understandable without verbal explanation, and consistent across text, numbers, and recommendations.

\begin{checkbox}
Do not hide delays, invent resources, remove essential testing, or present an AI-generated recommendation that the team cannot defend.
\end{checkbox}

\section{3. Executive Status}

\begin{tabularx}{\textwidth}{>{\bfseries}p{4cm} Y}
Overall status & $\square$ Green \quad $\square$ Amber \quad $\square$ Red \\[4mm]
Reporting point & Week: \underline{\hspace{2cm}} \quad Prepared by: \underline{\hspace{6cm}} \\[4mm]
One-sentence status & \blankline \\
\end{tabularx}

\vspace{4mm}
\begin{center}
\begin{tabularx}{\textwidth}{>{\bfseries}Y >{\centering\arraybackslash}p{2.5cm} >{\centering\arraybackslash}p{2.5cm} Y}
\toprule
Indicator & Planned & Actual / forecast & Meaning \\
\midrule
Progress & & & \\[6mm]
Cost & & & \\[6mm]
Modules & & & \\[6mm]
Critical defects & & & \\
\bottomrule
\end{tabularx}
\end{center}

\section{4. Problem and Cause}

\textbf{Verified problem:}

\vspace{8mm}\blankline

\textbf{Evidence:}

\vspace{8mm}\blankline

\textbf{Root cause, contributing cause, or current uncertainty:}

\vspace{8mm}\blankline

\section{5. Impact Assessment}

\begin{center}
\small
\begin{tabularx}{\textwidth}{>{\bfseries}p{2.5cm} Y Y}
\toprule
Dimension & Current impact & Expected consequence without action \\
\midrule
Scope & & \\[6mm]
Schedule & & \\[6mm]
Cost & & \\[6mm]
Quality / security & & \\[6mm]
Stakeholders & & \\[6mm]
Team capacity & & \\
\bottomrule
\end{tabularx}
\end{center}

\section{6. Corrective-Action Plan}

\begin{center}
\small
\begin{tabularx}{\textwidth}{>{\bfseries}p{1.8cm} Y p{3cm} p{2.2cm} Y}
\toprule
Action & Specific change & Owner & Deadline & Success evidence \\
\midrule
Stop & & & & \\[8mm]
Start & & & & \\[8mm]
Continue & & & & \\[8mm]
Escalate & & & & \\
\bottomrule
\end{tabularx}
\end{center}

\section{7. Revised Pilot Scope}

\begin{center}
\begin{tabularx}{\textwidth}{Y Y Y}
\toprule
Protect for week 12 & Defer after pilot & Requires sponsor decision \\
\midrule
 & & \\[14mm]
 & & \\
\bottomrule
\end{tabularx}
\end{center}

Explain the trade-off in one sentence:

\vspace{8mm}\blankline

\section{8. Recovery Milestones}

\begin{center}
\begin{tabularx}{\textwidth}{>{\bfseries}p{2cm} Y Y}
\toprule
Week & Required milestone & Acceptance evidence \\
\midrule
9 & & \\[7mm]
10 & & \\[7mm]
11 & & \\[7mm]
12 & & \\
\bottomrule
\end{tabularx}
\end{center}

\section{9. Monitoring and Escalation}

\begin{center}
\small
\begin{tabularx}{\textwidth}{Y p{2.5cm} Y Y}
\toprule
Indicator & Target & Escalation threshold & Response if threshold is crossed \\
\midrule
Integration tests passing & & & \\[7mm]
Critical bugs open & & & \\[7mm]
Schedule progress & & & \\[7mm]
Cost forecast & & & \\
\bottomrule
\end{tabularx}
\end{center}

\section{10. Sponsor Decision Request}

Use a decision statement, not a general request for support.

\begin{activitybox}
By \underline{\hspace{2cm}} (date/time), the PMO requests approval to \underline{\hspace{5cm}} because \underline{\hspace{5cm}}. If approval is not received, the expected consequence is \underline{\hspace{5cm}}.
\end{activitybox}

\section{11. Three-Minute Presentation Plan}

\begin{center}
\begin{tabularx}{\textwidth}{>{\bfseries}p{2.5cm} p{3cm} Y}
\toprule
Time & Speaker & Message \\
\midrule
0:00--0:30 & & Status and problem \\[6mm]
0:30--1:15 & & Evidence and impact \\[6mm]
1:15--2:15 & & Corrective actions and milestones \\[6mm]
2:15--3:00 & & Sponsor decision and consequences \\
\bottomrule
\end{tabularx}
\end{center}

\section{12. Quality Review and Rubric}

Before presenting, exchange the draft with another team and check:

\begin{itemize}
  \item[$\square$] Claims match the supplied evidence.
  \item[$\square$] Assumptions and uncertainties are labeled.
  \item[$\square$] Actions have owners, deadlines, and success measures.
  \item[$\square$] Scope choices protect essential pilot value.
  \item[$\square$] Testing, security, and transparent reporting remain present.
  \item[$\square$] The sponsor request is specific and decision-ready.
\end{itemize}

\begin{center}
\begin{tabularx}{\textwidth}{>{\bfseries}p{4cm} Y >{\centering\arraybackslash}p{2cm}}
\toprule
Criterion & Evidence expected & Points \\
\midrule
Evidence and diagnosis & Accurate status, indicators, causes, and impacts & 5 \\
Corrective-action quality & Feasible, prioritized, owned, and time-bound actions & 5 \\
Control logic & Useful targets, thresholds, and escalation responses & 5 \\
Sponsor communication & Clear trade-off, decision request, and consequence & 5 \\
Professional product & Concise, consistent written and oral briefing & 5 \\
\midrule
Total & & 25 \\
\bottomrule
\end{tabularx}
\end{center}

\section{13. Responsible AI Boundary}

AI may help improve structure, clarity, or visual presentation after the team creates the evidence and recommendation. The team must verify every number, disclose meaningful AI assistance when requested, and remain able to defend every sentence.

\vfill
\begin{center}\small\color{pmoTeal}Course portal: \href{https://maoude.github.io/teaching-ai-pmo/}{maoude.github.io/teaching-ai-pmo/}\end{center}
\end{document}
